### 2022-04-20 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@f6794af7cdf35fdcb3aa85893d1c3ce5eb4daa84 🚀

where X is \(atan(cos(deg2rad(60.0)), sin(deg2rad(60.0)))\), a constant
approximately equal to \(0.5235\).

@@

Higher host diversity may not result in a higher viral diversity; for
this reason, we quantified and mapped the evolutionary distinctiveness
of betacoronaviruses, based on \ldots. Viral evolutionary
distinctiveness largely tracks host diversity, particularly in southern
China but oddly not throughout the rest of southeast Asia, perhaps
indicating that many distinctive viruses remain to be discovered in this
region (an idea that is unsurprising given the growing realization,
around the emergence of SARS-CoV-2, that a unique lineage of similar
viruses are widespread in bats but still mostly undescribed). The most
distinct betacoronaviruses are found in South America, a region with a
comparatively lower number of hosts; this suggests that the South
American bat-betacoronvirus complex has been more isolated, and is
probably undergoing a different co-evolutionary dynamic. Alternatively,
this distinctiveness hostpot may be a product of under-sampling:
South-America is one of the places where the fewest betacoronaviruses
have been discovered (Anthony et al., 2017), and adding more viruses
would bring the distinctiveness of known sequences down. Previous work
has suggested the Americas may be a hotspot of both undiscovered bat
viruses in general (Olival) and coronavirus specifically (Anthony),
though not necessarily betacoronaviruses, and particularly not those in
clades with notable zoonotic potential (c.f. Anthony).

@@

>>>>

where X is
\(\text{atan}\left(\text{cos}(\text{rad}(60)), \text{sin}(\text{rad}(60))\right)\),
a constant approximately equal to \(0.5235\).

@@

Higher host diversity may not result in a higher viral diversity; for
this reason, we quantified and mapped the evolutionary distinctiveness
of betacoronaviruses, based on \ldots. Viral evolutionary
distinctiveness largely tracks host diversity, particularly in southern
China but oddly not throughout the rest of southeast Asia, perhaps
indicating that many distinctive viruses remain to be discovered in this
region (an idea that is unsurprising given the growing realization,
around the emergence of SARS-CoV-2, that a unique lineage of similar
viruses are widespread in bats but still mostly undescribed). The most
distinct betacoronaviruses are found in South America, a region with a
comparatively lower number of hosts; this suggests that the South
American bat-betacoronvirus complex has been more isolated, and is
probably undergoing a different co-evolutionary dynamic. Alternatively,
this distinctiveness hostpot may be a product of under-sampling:
South-America is one of the places where the fewest betacoronaviruses
have been discovered (Anthony et al. 2017), and adding more viruses
would bring the distinctiveness of known sequences down. Previous work
has suggested the Americas may be a hotspot of both undiscovered bat
viruses in general (Olival et al. 2017, Allen et al. 2017) and
coronavirus specifically (Anthony et al. 2017), though not necessarily
betacoronaviruses, and particularly not those in clades with notable
zoonotic potential.

@@

\leavevmode\hypertarget{ref-Allen2017GloHot}{}%
Allen, T. et al. 2017. Global hotspots and correlates of emerging
zoonotic diseases. - Nature Communications in press.
